{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-05-29 thesis/education.tex
pintos testce

@@

For this study students were recruited remotely via email.
After each of the Threads and Userprog project deadlines (\sect{\ref{sec:overview-pintos}}),
% TODO talk about th econtence of the email

@@

% prisema
% alarm simul
% donate multiple
% wait simple

>>>>

The tests can all be viewed at \url{https://github.com/bblum/landslide/tree/master/pebsim/p2-basecode/410user/progs}.

@@

For this study students were recruited remotely via email.
After each of the {\em threads} and {\em userprog} project deadlines (\sect{\ref{sec:overview-pintos}}),
% TODO talk about th econtence of the email

@@

Like the P2 tests, the Pintos test cases are either hand-picked from the provided unit tests,
with an eye for which will produce interesting concurrent behaviour,
or created using a TA's intuition for the most likely student bugs.
The following tests are approved to be Landslide-friendly:

\begin{itemize}
	\item {\tt priority-sema}:
		Modified to be Landslide-friendly from the basecode, for {\em threads}.
		Creates two child threads to wait on a semaphore and signals them.
		Replaces threads with different priorities
		(originally chosen to produce deterministic output which the test checked for)
		with threads of the same priority.
	\item {\tt alarm-simultaneous}:
		Modified to be Landslide-friendly from the basecode, for {\em threads}.
		Creates two child threads which each invoke {\tt timer\_sleep()} for a different amount of time.
		Number of (threads,iterations) reduced from (3,5) to (2,1).
	\item {\tt wait-simple}:
		Unmodified from the basecode's version, for {\em userprog}.
		Userspace process {\tt exec()}s a child process, which immediately exits, and {\tt wait()}s on it.
	\item {\tt priority-donate-multiple}:
		Written by Kevin Zhao, TA at U. Chicago, for {\em threads}.
		Tests for a priority donation race during {\tt lock\_release()}
		in which a thread holding a lock can accidentally keep a contending thread's donated priority
		after finishing releasing it.
\end{itemize}

The (unpatched versions of) the first three tests are available at
\url{https://github.com/Berkeley-CS162/group0/tree/master/pintos/src/tests}.
The fourth test is available at
% FIXME: allowbreak makes nasty latex shit show up in the output??
\url{https://github.com/bblum/landslide/blob/master/pebsim/pintos/priority-donate-multiple.c}.

### 2018-05-29 thesis/overview.tex
pintos testce

Some schools further offer a virtual memory project, extending the provided VM with a frame table and supplemental page table and fault handler \cite{standford-cs140,uchicago-cs230}, or supplemental HTTP server and {\tt malloc} assignments \cite{berkeley-cs162}.
Being largely architectural/algorithmic projects rather than concurrency-oriented ones, I am not concerned with these assignments in this thesis.
The main concurrency challenges in Pintos projects arise from the threads and userprog assignments:
implementing a correct {\tt alarm} routine,
ensuring the priority scheduler remains safe in the presence of concurrent threads of the same priority,
and designing correct interactions between the {\tt wait} and {\tt exit} system calls.

>>>>

Some schools further offer a virtual memory project, extending the provided VM with a frame table and supplemental page table and fault handler \cite{standford-cs140,uchicago-cs230}, or supplemental HTTP server and {\tt malloc} assignments \cite{berkeley-cs162}.
Being largely architectural/algorithmic projects rather than concurrency-oriented ones, I am not concerned with these assignments in this thesis.
The main concurrency challenges in Pintos projects arise from the {\em threads} and {\em userprog} assignments:
implementing a correct {\tt alarm} routine,
ensuring the priority scheduler remains safe in the presence of concurrent threads of the same priority,
and designing correct interactions between the {\tt wait} and {\tt exit} system calls.
